Distributions

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Good! I like these figures.

# What values to use
map_dbl(cp.best[,-c(1,2)], min, na.rm = TRUE)
map_dbl(cp.best[,-c(1,2)], max, na.rm = TRUE)
map_dbl(pp.best[,-c(1:3)], min, na.rm = TRUE)
map_dbl(pp.best[,-c(1:3)], max, na.rm = TRUE)
map_dbl(np.best[,c(4:8)], min, na.rm = TRUE)
map_dbl(np.best[,c(4:8)], max, na.rm = TRUE)

>>>>

# What values to use
# map_dbl(cp.best[,-c(1,2)], min, na.rm = TRUE)
# map_dbl(cp.best[,-c(1,2)], max, na.rm = TRUE)
# map_dbl(pp.best[,-c(1:3)], min, na.rm = TRUE)
# map_dbl(pp.best[,-c(1:3)], max, na.rm = TRUE)
# map_dbl(np.best[,c(4:8)], min, na.rm = TRUE)
# map_dbl(np.best[,c(4:8)], max, na.rm = TRUE)
